Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-05-29 LaTeX_paper/paper.tex
LaTeX: finish general structure of algorithms

\usepackage[a4paper, total={6.5in, 9in}]{geometry}

@@

@@

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle [\ref{fig:figure_digital_puzzle}],
but there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle [\ref{fig:figure_real_puzzle}].\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a paper,
this wants to be the first.\newline
As a bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

@@

All the algorithms that will be analyzed are composed of 3 sub algorithms.

>>>>

% to set the margin of the page
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% to make indentations
\usepackage{changepage}

@@

% settings for how to indend the page when neaded
\newenvironment{indented_section}
  {\adjustwidth{3em}{0pt}}
  {\endadjustwidth}

@@

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle \ref{fig:figure_digital_puzzle},
but there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle \ref{fig:figure_real_puzzle}.\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a full paper,
this wants to be the first.\newline
As a bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

@@

All the algorithms that will be analyzed are composed of 3 sub algorithms:

\begin{indented_section}

    \subsubsection{The Splitter:} This component takes as input one or more images
    containing all the pieces. It then split all the pieces from each other,
    9and split each piece into his four sides.\label{document:splitter}

    \subsubsection{The Comparator:} This component compares each side with all the
    others, in order to understand whether they match or not.\newline
    There are two distinct kinds of “Comparator” algorithms:
    The “Binary Comparison” and the “Non Binary Comparison”.
    As the name suggests when comparing two sides with a “Binary Comparison”
    the result can either be 0 (they do not match) or 1 (they match).
    In contrast a “Non Binary Comparison” can give any value between 0 and 1.
    This allows states of uncertainty to be represented.\label{document:comparator}

    \subsubsection{The Solver:} This component  uses the information provided by the
    Comparator \ref{document:comparator}, and tries to find a solution
    (i.e.\ a position and an orientation for each piece)
    that is the most likely to be correct.\label{document:solver}

\end{indented_section}

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian}
